\speculake: Hiding Malware in Speculative Execution

### 2018-12-01 paper/figures.tex
add table

\newcommand{\FigHighLevel}{
\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-trimmed.pdf}
    \caption{\textbf{\speculake}\,---\,%
    Both the trigger and payload binaries exhibit the same initial series of
    indirect jumps (Step 1). The trigger program solely executes these
    jumps to (mis)train the branch predictor. In the Payload program
    \texttt{fn\_ptr} has been set to point to the \texttt{cache\_timing}
    function and flushed from cache. Thus the branch predictor
    mis-predicts the jump to \texttt{cache\_timing} and instead jumps to
    \texttt{target\_fn} (Step 2) as trained by the trigger program (green line). 
    \texttt{target\_fn} then executes speculatively (Step 3), until
    \texttt{fn\_ptr} is loaded from memory and the processor redirects
    computation to the \texttt{cache\_timing} function (Step 4),
    which measures which value was speculatively loaded into cache.}
    \label{fig:high-level}

@@

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
        \includegraphics[width=0.4\textwidth]{figures/ExSpectre_CR_key.png}
        \caption{\textbf{ExSpectre model}\,---\,%
        General model of speculative computation within the payload 
        process when triggered. The \textit{Speculative Gadget} has read-only
        access to all memory within the process, but can return updates/results via a
        cache side channel (via access to the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the \textit{Real World} process.}
    \label{fig:general_model}
\end{figure}
}

@@

>>>>

\newcommand{\FigHighLevel}{
\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-new.pdf}
    \includegraphics[width=0.4\textwidth]{figures/ExSpectre_CR_key.png}
    \caption{\textbf{\speculake}\,---\,%
    Both the trigger and payload binaries exhibit the same initial series of
    indirect jumps (Step 1). The trigger program solely executes these
    jumps to (mis)train the branch predictor. In the Payload program
    \texttt{fn\_ptr} has been set to point to the \texttt{cache\_timing}
    function and flushed from cache. Thus the branch predictor
    mis-predicts the jump to \texttt{cache\_timing} and instead jumps to
    \texttt{target\_fn} (Step 2) as trained by the trigger program (green line). 
    \texttt{target\_fn} then executes speculatively (Step 3), until
    \texttt{fn\_ptr} is loaded from memory and the processor redirects
    computation to the \texttt{cache\_timing} function (Step 4),
    which measures which value was speculatively loaded into cache.}
    \label{fig:high-level}

@@

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
        \caption{\textbf{ExSpectre model}\,---\,%
        General model of speculative computation within the payload 
        process when triggered. The \textit{Speculative Gadget} has read-only
        access to all memory within the process, but can return updates/results via a
        cache side channel (via access to the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the \textit{Real World} process.}
    \label{fig:general_model}
\end{figure}
}

@@

\newcommand{\processorTable}{
\begin{table}
    \centering
    \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{l X X| Y Y Y}
        Processor & Year\newline
        released & Micro\newline
        arch & Nested\newline 
        Spec? & Num\newline
        indirect jumps* & Max $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & ?  & ?  \\
        AMD EPYC 7251             & 2017 & Ryzen   &            & ?  & ?  \\
    \end{tabularx}}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel and one AMD processor. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}) though
    the older Haswell processor and the AMD processor were not. We found that
    the Intel Xeon CPU E3-1270 v6 required 28 identical indirect jumps in the
    trigger and payload programs to reliably enter the speculative world at the
    desired address ($> 95\%$) while the Intel Core i5-7200U only required 26
    jumps.}
    \label{table:processors}
\end{table}
}
